Motional Quantum Ground-State Cooling Outside the Lamb-Dicke Regime -- Supplemental material

### 2017-08-03 sequence.tex
Figure tweaks

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$n$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!n-1\!)$-th}\\\textbf{order}};
    }

>>>>

    %% Axial
    \foreach \i in {0,...,7} {
      \fill[blue!30]
      plot[draw,samples=200,domain={2.8*\i}:{2.8*\i+1.6},variable=\x] ({\x}, {sin((\x-2.8*\i) * 112.5)^4})
      -- cycle;
      \draw[line width=1,blue] plot[domain={2.8*\i}:{2.8*\i+1.6},variable=\x]
      ({\x}, {sin((\x-2.8*\i) * 112.5)^4}) -- (2.8*\i + 2.8, 0);
    }
    \path[blue] (2.8*2+0.8, 1) node[above,align=center] {\textit{Axial $z$}};
    \foreach \i in {0,...,3} {
      \path (5.6*\i + 0.8, -0.15) node[below,blue,align=center] {\textbf{$m$-th}\\\textbf{order}};
      \path (5.6*\i + 3.6, -0.15) node[below,blue,align=center] {\textbf{$(\!m-1\!)$-th}\\\textbf{order}};
    }
